---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# QTExpTool

<!-- badges: start -->
[![GitHub issues](https://img.shields.io/github/issues/AliSajid/QTExpTool)](https://github.com/AliSajid/QTExpTool/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/AliSajid/QTExpTool)](https://github.com/AliSajid/QTExpTool/pulls)
<!-- badges: end -->

The goal of `QTExpTool` is to provide an alternative way of evaluating 
    differential gene expression.
    
This tool uses the gene expression data generated from any standard
gene expression pipeline and returns whether a gene is over-expressed
or under-expressed on a five point likert-type scale. The goal for this
representation is to make the gene expression more clinically relevant
to physicians and other non-bioinformatics specialists that are only
interested in the qualitative judgement of changes in gene expression.

## Installation instructions

Get the latest stable `R` release from [CRAN](http://cran.r-project.org/). Then install `QTExpTool` from [Bioconductor](http://bioconductor.org/) using the following code:

```{r 'install', eval = FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE)) {
    install.packages("BiocManager")
}

BiocManager::install("QTExpTool")
```

And the development version from [GitHub](https://github.com/AliSajid/QTExpTool) with:

```{r 'install_dev', eval = FALSE}
BiocManager::install("AliSajid/QTExpTool")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval = requireNamespace('QTExpTool')}
library("QTExpTool")
## basic example code
```

## Citation

Below is the citation output from using `citation('QTExpTool')` in R. Please
run this yourself to check for any updates on how to cite __QTExpTool__.

```{r 'citation', eval = requireNamespace('QTExpTool')}
print(citation('QTExpTool'), bibtex = TRUE)
```

Please note that the `QTExpTool` was only made possible thanks to many other R and bioinformatics software authors, which are cited either in the vignettes and/or the paper(s) describing this package.

## Code of Conduct

Please note that the `QTExpTool` project is released with a [Contributor Code of Conduct](http://bioconductor.org/about/code-of-conduct/). By contributing to this project, you agree to abide by its terms.

## Development tools

* Continuous code testing is possible thanks to [GitHub actions](https://www.tidyverse.org/blog/2020/04/usethis-1-6-0/)  through `r BiocStyle::CRANpkg('usethis')`, `r BiocStyle::CRANpkg('remotes')`, and `r BiocStyle::CRANpkg('rcmdcheck')` customized to use [Bioconductor's docker containers](https://www.bioconductor.org/help/docker/) and `r BiocStyle::Biocpkg('BiocCheck')`.
* Code coverage assessment is possible thanks to [codecov](https://codecov.io/gh) and `r BiocStyle::CRANpkg('covr')`.
* The [documentation website](http://AliSajid.github.io/QTExpTool) is automatically updated thanks to `r BiocStyle::CRANpkg('pkgdown')`.
* The code is styled automatically thanks to `r BiocStyle::CRANpkg('styler')`.
* The documentation is formatted thanks to `r BiocStyle::CRANpkg('devtools')` and `r BiocStyle::CRANpkg('roxygen2')`.

For more details, check the `dev` directory.

This package was developed using `r BiocStyle::Biocpkg('biocthis')`.


